---
title: "Carrefour Kenya"
author: "Christine Muthee"
date: "12/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Marketing Analysis.

## 1. Main objective: 
#### * Getting the most relevant marketting strategies that will result in the highest number of sales ( Total price tax inclusive)
### Specific Objectives
#### * Reduce highly dimensional datasets to lower dimensions for easier interpratability and analysis while assessing the attributes carrying core information in our dataset.
#### * Getting important attributes from the dataset.
#### * Getting associations within the transactions that will uncover important relationships for effective marketing.
#### * Checking for anomalies in the sales dataset for the sole purpose of fraud detection.

## 2. Data Inspection.
```{r}
library(data.table)
part1_df<-fread("http://bit.ly/CarreFourDataset")
head(part1_df)
```
#### Checking for missing values 

```{r}
# Checking for missing values
any(is.na.data.frame(part1_df))
# There are no missing values
```
#### Checking for duplicated values

```{r}
# Checing for duplicated data
any(duplicated.data.frame(part1_df))
# There are no duplicates in our dataset
```
#### Encoding categorical variables to nominal to perform PCA
```{r}
library("dbplyr")

numerical<-select_if(part1_df,is.numeric)
numerical
```
```{r}
str(part1_df)
```
```{r}
?dummyVars
```

```{r}
# Selecting non numeric columns
head(part1_df)
# Caret package for dummy variables
library(caret)
# Encoding using Dummy variables and excluding unique ID and date time data
dums<-dummyVars("~.",data=part1_df[,c(-1,-9,-10)])
dums
# Encoding.
new_df<-data.frame(predict(dums,newdata =part1_df[,c(-1,-9,-10)]))
new_df
```
```{r}
?prcomp
```

```{r}
# Dimensionality Reduction technique
# Will use PCA so as to understand the variance displayed by each feature
reduced_df<-prcomp(new_df,center = TRUE)
reduced_df$sdev

```

```{r}

```

```{r}

```








